---
title: "netANT pipeline project"
author: "Jared P. Zimmerman + Benjamin L. Deck"
date: "5/1/2019"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
    number_sections: false
    code_folding: 'hide'
    theme: 'cosmo'
---

```{r setup, include= FALSE, results= "hide", message= FALSE, error= FALSE}

# load packages with the pacman package
if(!require('pacman')) {
  install.packages('pacman')
}
pacman::p_load(dplyr, ggplot2, wesanderson, tidyr, reshape2, tools)
```


```{r, results= 'hide', echo=F, include= FALSE, message= FALSE, error= FALSE}
dataDir <- '/Users/Ben/Google Drive/CogNeW Laboratory Files/Projects/Net-ANT/Net-ANT Task/Data/FPCN_cTBS/'
datFiles <- list.files(path = dataDir, pattern = '*\\.txt',
                       recursive = T, full.names = T)
datFiles
```

```{r, results= 'hide', echo=F}
source('/Users/Ben/Google Drive/CogNeW Laboratory Files/Projects/Net-ANT/Net-ANT Task/Data/scripts/processSingleSubANTdataforce.R')

dat.list <- lapply(datFiles, function(d) {
  sesh <- regmatches(d, regexpr(d, pattern = '(pre|post)'))
  id <- regmatches(d, regexpr(d, pattern = '[0-9]{3}'))
  data <- processSingleSubANT(d)
  output <- bind_cols(tibble(id = id), tibble(sesh = sesh), data)
  return(output)
})
df <- bind_rows(dat.list)
df
```


```{R, results = 'hide', echo = F}
df$sesh <- factor(df$sesh, levels = c('pre','post'))


```


# ANT efficiency calculations
```{r}
 df <- df %>%
  dplyr::mutate(Fan2002Alert = (no_medRT - center_medRT)) %>%
  dplyr::mutate(Fan2002Orient = (center_medRT - spatial_medRT)) %>%
  dplyr::mutate(Fan2002Executive = incongruent_medRT - congruent_medRT) %>%
  dplyr::mutate(Fan2003Alert = (Fan2002Alert / medRT)) %>%
  dplyr::mutate(Fan2003Orient = (Fan2002Orient / medRT)) %>%
  dplyr::mutate(Fan2003Executive = Fan2002Executive / medRT) %>%
  dplyr::mutate(CognewAlert = (Fan2002Alert/ no_medRT)) %>%
  dplyr::mutate(CognewOrient = (Fan2002Orient / center_medRT)) %>%
  dplyr::mutate(CognewExecutive = (Fan2002Executive / congruent_medRT)) %>%
  dplyr::mutate(ChinaAlert = (Fan2002Alert / center_medRT)) %>%
  dplyr::mutate(ChinaOrient = (Fan2002Orient / spatial_medRT)) %>%
  dplyr::mutate(ChinaExecutive = (Fan2002Executive / congruent_medRT))
  
```


```{r, results='hide', echo=FALSE}
lapply(datFiles, function(d) {
  id <- regmatches(d, regexpr(d, pattern = '[0-9]{3}'))
  id
})
```


```{r, results='hide', echo=F}
datFiles
```

```{R, results = 'hide', echo = F}

df2 <- melt(df, sesh = 'sesh')
df3 <- df2 %>%
  dplyr::arrange(sesh) %>%
  dplyr::filter(variable == 'congruent_medRT' | variable == "incongruent_medRT" | 
                  variable == 'center_medRT'
                | variable == 'spatial_medRT' | variable == 'no_medRT')

df3 



```


# Plot of median RT distributions
```{R}

MedianRTDistribution_plot <-  ggplot(df3, aes(x = variable, y = value, fill =sesh)) +
  geom_boxplot(varwidth = T) + 
      labs(title= " L-DAN target Median Distribution of each trial type",
           x = 'Trial type',
           y = 'Median RT') +
  scale_x_discrete(labels(c('Congruent', 'Incongruent', 'Center Cue', 'No Cue', 'Spatial Cue'))) +
             theme(axis.text.x = element_text(angle=45, vjust = .9))
MedianRTDistribution_plot



```



# Alerting

## Fan 2002 alerting plot median(no cue - center cue)
```{R}

require(ggplot2)



Fan2002Alert_plot <- ggplot(df, aes(x = sesh, y = Fan2002Alert))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Fan 2002 Alerting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
Fan2002Alert_plot
```

## Fan 2003 alert median ((no cue - center cue)/median RT of all trials)
```{R}
Fan2003Alert_plot <- ggplot(df, aes(x = sesh, y = Fan2003Alert))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Fan 2003 Alerting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
Fan2003Alert_plot
```


## Cognew Alert median ((no cue - center cue) / no cue) 
``` {R}
CognewAlert_plot <- ggplot(df, aes(x = sesh, y = CognewAlert))  +
  geom_boxplot( fill= c('royalblue',"white"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Cognew Alerting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
CognewAlert_plot

```


## China alert median ((no cue - center cue )/ center cue)
```{R}
ChinaAlert_plot <-  ggplot(df, aes(x = sesh, y = ChinaAlert))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " China-Group Alerting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
ChinaAlert_plot

```

## Alerting matrix plots

```{R}
df %>% dplyr::select(id, sesh, contains("alert")) %>%
 melt(., id.vars = c('id', 'sesh')) %>%
 ggplot(aes(x = 1, y = value, fill = sesh)) +
 geom_boxplot() +
 facet_wrap(~variable, scale = 'free_y')


```

## Alerting Dot plot-- Showing change in alerting pre tms to post tms per person--- uses cognew alerting

```{R, echo =F}
df %>%
 ggplot(aes(x = sesh, y = CognewAlert, color = id, group = id)) +
 geom_point() +
 geom_line() #+ facet_wrap(~Retrieval)

```


# Orienting

## Fan 2002 Orienting median(center cue - spatial cue)
``` {R}
Fan2002Orient_plot <- ggplot(df, aes(x = sesh, y = Fan2002Orient))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Fan 2002 Orienting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
Fan2002Orient_plot

```

## Fan 2003 orient median ((center cue - spatial cue) /median RT of all trials) 
```{R}

Fan2003Orient_plot <- ggplot(df, aes(x = sesh, y = Fan2003Orient))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Fan 2003 Orienting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
Fan2003Orient_plot

```


## Cognew Orient median ((center cue - spatial cue)/ center cue)
```{R}
CognewOrienting_plot <- ggplot(df, aes(x = sesh, y = CognewOrient))  +
  geom_boxplot( fill= c('royalblue',"white"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Cognew Orienting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
CognewOrienting_plot
```


## China Orienting median ((center cue - spatial cue) / spatial cue)
```{R}

ChinaOrient_plot <-  ggplot(df, aes(x = sesh, y = ChinaOrient))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " China-group Orienting ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
ChinaOrient_plot
```


## Orienting matrix plots

```{R}
df %>% dplyr::select(id, sesh, contains("Orient")) %>%
 melt(., id.vars = c('id', 'sesh')) %>%
 ggplot(aes(x = 1, y = value, fill = sesh)) +
 geom_boxplot() +
 facet_wrap(~variable, scale = 'free_y')


```


## Median orienting dot plot --- showing change in orienting per person from pre tms to post tms--Uses cognew orienting

``` {R }
df %>%
 ggplot(aes(x = sesh, y = CognewOrient, color = id, group = id)) +
 geom_point() +
 geom_line() #+ facet_wrap(~Retrieval)

```


# Executive


## Fan 2002 executive median(Incongruent - congruent)
``` {R}
Fan2002Executive_plot <- ggplot(df, aes(x = sesh, y = Fan2002Executive))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Fan 2002 Executive ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
Fan2002Executive_plot
```


## Fan 2003 executive median ((incongruent - congruent) / median RT of all trials))
```{R}
Fan2003Executive_plot <- ggplot(df, aes(x = sesh, y = Fan2003Executive))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Fan 2003 Executive ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
Fan2003Executive_plot
```


## Cognew Executive median ((incongruent - congruent) / congruent )
``` {R}
CognewExecutive_plot <- ggplot(df, aes(x = sesh, y = CognewExecutive))  +
  geom_boxplot( fill= c('royalblue',"white"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " Cognew Executive Efficiency", x = 'Session') +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
CognewExecutive_plot
```


## China Executive median ((incongurent - congruent ) / congruent)
``` {R}

ChinaExecutive_plot <-  ggplot(df, aes(x = sesh, y = ChinaExecutive))  +
  geom_boxplot( fill= c('orange',"tomato"), show.legend = T, notch = F, na.rm = T) + 
      labs(title= " China-Group Executive ") +
    scale_x_discrete(labels = c("Pre", "Post")) +
  #scale_y_continuous(breaks=seq(-.05, .2, .03), limits = c(-.05, .2)) +
             theme(axis.text.x = element_text(angle=65, vjust=0.3))
ChinaExecutive_plot


```







``` {R, results= 'hide', echo = F}
df %>%
  dplyr::group_by(sesh) %>%
    dplyr::summarise(medRT = median(CognewExecutive),
                     nTrials = n()) %>%
    tidyr::gather(variable, value, medRT:nTrials) %>%
    unite(temp, sesh, variable) %>%
    tidyr::spread(temp, value)





```


## Executive matrix plots
```{R}

df %>% dplyr::select(id, sesh, contains("exec")) %>%
 melt(., id.vars = c('id', 'sesh')) %>%
 ggplot(aes(x = 1, y = value, fill = sesh)) +
 geom_boxplot() +
 facet_wrap(~variable, scale = 'free_y')


```


## Median executive pre tms – showing change in executive pre tms to post tms per person --- uses cognew executive

```{R}
df %>%
 ggplot(aes(x = sesh, y = CognewExecutive, color = id, group = id)) +
 geom_point() + labs(x = 'Session', title = 'Cognew Executive Efficiency Change') +
 geom_line() #+ facet_wrap(~Retrieval)


```


## Median change in no cue trial from pre tms to post tms per person

```{R}
df %>%
 ggplot(aes(x = sesh, y = no_medRT, color = id, group = id)) +
 geom_point() +
 geom_line() #+ facet_wrap(~Retrieval)

```



# T-tests of pre and post efficiency measures

```{R}
execT <- df  %>%
  dplyr::group_by(sesh) %>%
  tidyr::spread(sesh, CognewExecutive) %>%
  dplyr::select(pre, post)

t.test(na.omit(execT$pre), na.omit(execT$post), paired = T, alternative = 'two.sided')

```



```{r}

df.cors.pre <- df %>%
  dplyr::group_by(sesh) %>%
  dplyr::filter(sesh == 'pre')

cor.test(df.cors.pre$CognewAlert, df.cors.pre$CognewOrient, alternative = 'two.sided', method = 'pearson')
cor.test(df.cors.pre$CognewAlert, df.cors.pre$CognewExecutive, alternative = 'two.sided', method = 'pearson')
cor.test(df.cors.pre$CognewOrient, df.cors.pre$CognewExecutive, alternative = 'two.sided', method = 'pearson')



```

```{r}
df.cors.post <- df %>%
  dplyr::group_by(sesh) %>%
  dplyr::filter(sesh == 'post')

cor.test(df.cors.post$CognewAlert, df.cors.post$CognewOrient, alternative = 'two.sided', method = 'pearson')
cor.test(df.cors.post$CognewAlert, df.cors.post$CognewExecutive, alternative = 'two.sided', method = 'pearson')
cor.test(df.cors.post$CognewOrient, df.cors.post$CognewExecutive, alternative = 'two.sided', method = 'pearson')


```

```{r}
lawstat::levene.test(df$CognewExecutive, df$sesh)

effsize::cohen.d(df$CognewExecutive, df$sesh, pooled=TRUE)



```